A Possibilistic Valid-time Model

### 2011-11-30 trunk/ipmu2012/preliminaries.tex
Some place-saving changes...

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory, like probability theory, deals with uncertainty about the outcome of an experiment. In probability theory, this uncertainty is caused by the \emph{variability} in the outcomes, while in possibility theory, the uncertainty is caused by \emph{incomplete knowledge} about the experiment. The quantification of confidence in probability theory is achieved by means of a measure of chance, whereas in possibility theory, possibility and necessity measures are used. In any case, the quantification of confidence in a theory of uncertainty is achieved using a confidence measure\cite{Shafer:1976:AMathematical}.

@@

In this work, an ill-known set will be defined and represented via its start and end point, which will be ill-known values. The correspondences and transitions between these two representations are part of the authors current research.

@@

A specific application of possibilistic variables is obtained when the universe under consideration is the set of boolean values $\mathbb{B}$ = $\{T,F\}$. Indeed, any boolean propositional variable $p$ takes just one value in $\mathbb{B}$. If the knowledge on which value this variable $p$ will take is given by a possibility distribution $\pi_p$, the variable can be seen as a possibilistic variable. As the interest lies with the case where the proposition holds, the possibility and necessity that $p$ = $T$ (the proposition holds) demands most attention. This possibility and necessity is noted here as:
\begin{align}
Pos(p) & = \pi_p(T) \label{propholdsposs} \\
Nec(p) & = 1-\pi_p(F) \label{propholdsnecc}
\end{align}
Here, notation \ref{propholdsposs} denotes the possibility that $p$ = $T$ and the proposition holds, notation \ref{propholdsnecc} denotes the necessity that $p$ = $T$ and the proposition holds.

@@

\subsubsection{Interval Evaluation by Ill-known Constraints}
The problem of the interval evaluation is explained in \cite{Pon11}: For a crisp interval $I = \left[ a, b \right]$, we want to know if all points in this interval reside between the boundaries of the ill-known interval $\left[ X , Y \right]$, where $X,Y$ are ill-known values on the set of real numbers $\mathbb{R}$, and $\lambda$ is the evaluation function.

>>>>

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory, like probability theory, deals with uncertainty about the outcome of an experiment. In probability theory, this uncertainty is caused by the \emph{variability} in the outcomes, while in possibility theory, the uncertainty is caused by \emph{incomplete knowledge} about the experiment. The quantification of confidence in a theory of uncertainty is achieved using a confidence measure\cite{Shafer:1976:AMathematical}. In probability theory this is a measure of chance, in possibility theory, possibility and necessity measures are used.

@@

This work will deal with ill-known intervals. These are ill-known sets, defined and represented via a start and end point, which will be ill-known values. The elements of the set are the values between the start and end point. An closed ill-known interval with start point $X$ and end point $Y$ is noted here $\left[X, Y\right]$. The correspondences and transitions between the representations of ill-known sets and between the representation of an ill-known set and an ill-known interval are part of the authors current research.

@@

A specific application of possibilistic variables is obtained when the universe under consideration is the set of boolean values $\mathbb{B}$ = $\{T,F\}$. Indeed, any boolean proposition $p$ takes just one value in $\mathbb{B}$. If the knowledge on which value this proposition $p$ will take is given by a possibility distribution $\pi_p$, the proposition can be seen as a possibilistic variable. As the interest lies with the case where the proposition holds, the possibility and necessity that $p$ = $T$ (the proposition holds) demands most attention. This possibility and necessity is noted here as:
\begin{align}
Pos(p) & = \pi_p(T) \label{propholdsposs} \\
Nec(p) & = 1-\pi_p(F) \label{propholdsnecc}
\end{align}
Here, notation \ref{propholdsposs} denotes the possibility that $p$ = $T$ and the proposition holds, notation \ref{propholdsnecc} denotes the necessity that $p$ = $T$ and the proposition holds.

@@

\subsubsection{Interval Evaluation by Ill-known Constraints}
The problem of interval evaluation is more generally explained in \cite{Pon11}: for a crisp interval $I = \left[a, b \right]$, the need exists to know if all points in this interval reside between the boundaries of an ill-known interval $\left[ X , Y \right]$.

The notion of an \emph{ill-known constraint} is introduced:

\begin{definition}
Given a universe $U$, an \emph{ill-known constraint} $C$ on a set $A \subseteq U$ is specified by means of a binary relation $R \subseteq U^{2}$ and a fixed, ill-known value denoted by its variable $X$ over $U$, i.e.:
\begin{align}
C \triangleq (R,X)
\end{align}
\end{definition}
